\documentclass[12pt]{res} % Use the res.cls style
\usepackage{enumitem, hanging}
\usepackage[top=.75in, left =.8in]{geometry}
\usepackage{booktabs}
\setlist[itemize]{leftmargin=0em}

\usepackage{helvet} ∫% Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
%\usepackage{tabularx}
\usepackage[colorlinks,linkcolor=blue,citecolor=blue,urlcolor=black,hyperfootnotes=false]{hyperref}
\newsectionwidth{0pt} % Stops section indenting

\begin{document}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

\name{{\LARGE Ivan Rudik}} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

\address{\textbf{Address}\\ 462 Warren Hall \\
Cornell University \\
Ithaca, NY 14853\vspace{.1in} } % Your address 1

\address{\textbf{Contact Information} \\
\href{mailto:irudik@cornell.edu}{irudik@cornell.edu} \\
\href{https://www.ivanrudik.com}{https://ivanrudik.com} \\
}
%----------------------------------------------------------------------------------------

\begin{resume}
\vspace{-0.08in}
\hrule
\vspace{-0.1in}
%----------------------------------------------------------------------------------------
%	Research Interests

%----------------------------------------------------------------------------------------
%	Education
%----------------------------------------------------------------------------------------
\subsection{Academic Appointment}

	%\vspace{4pt} % Gap between title and text

	\begin{itemize} \itemsep -12pt
	\item[] Cornell University
		\vspace{-0.05in}
		\begin{itemize} \itemsep -1pt
			\item[] Ruth and William Morgan Assistant Professor \hfill 2020--
			\item[] Assistant Professor, Dyson School of Applied Economics and Management \hfill 2018--
			\item[] Faculty Fellow, Atkinson Center for a Sustainable Future \hfill 2018--\\\
		\end{itemize}
		\item[] Iowa State University
		\vspace{-0.05in}
		\begin{itemize} \itemsep -1pt
			\item[] Assistant Professor, Department of Economics \hfill 2015--2017
			\item[] Center For Agricultural and Rural Development \hfill 2015--2017 \\\
		\end{itemize}
		\vspace{-0.075in}
	\end{itemize}
\vspace{-0.5in}
%----------------------------------------------------------------------------------------
%	Education
%----------------------------------------------------------------------------------------
\subsection{Education}

	%\vspace{4pt} % Gap between title and text

	\begin{itemize}
		\item[] Ph.D., Economics \hfill 2015\\
		University of Arizona

		\item[] M.A., Economics \hfill 2011\\
		University of Arizona

		\item[] B.S.,  Economics \hfill 2010\\
		Rochester Institute of Technology

	\end{itemize}
\vspace{-.2in}
\subsection{Publications}
\begin{itemize}
	\item[] Hollingsworth, A. and I. Rudik. 2021. \href{https://osf.io/preprints/socarxiv/rdy6g}{The Effect of Leaded Gasoline on Elderly Mortality: Evidence from Regulatory Exemptions}. \textbf{American Economic Journal: Economic Policy} 13(3):1--32.
	\item[] Liang, Y., I. Rudik, E. Zou, A. Johnston, A. Rodewald, C. Kling. 2020. \href{https://www.pnas.org/content/early/2020/11/23/2013568117}{Conservation Co-Benefits from Pollution Regulation: Evidence from Birds.} \textbf{Proceedings of the National Academy of Sciences} 117(49):30900--30906.
	\item[] Lade, G. and I. Rudik. 2020. \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3086728}{Costs of Inefficient Regulation: Evidence from the Bakken}. \textbf{Journal of Environmental Economics and Management}: 102336.
	\item[] Rudik, I. 2020. \href{https://www.aeaweb.org/articles?id=10.1257/pol.20160541}{Optimal Climate Policy When Damages are Unknown}. \textbf{American Economic Journal: Economic Policy} 12(2):340--73.
	\item[] Hollingsworth, A. and I. Rudik. 2019. \href{http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2697222}{External Impacts of Local Energy Policy: The Case of Renewable Portfolio Standards}. \textbf{Journal of the Association of Environmental and Resource Economists} 6(1):187--213.
	\item[] Keiser, D., G. Lade, and I. Rudik. 2018. \href{http://advances.sciencemag.org/content/4/7/eaat1613}{Air Pollution and Visitation at U.S. National Parks}. \textbf{Science Advances} 4(7):eaat1613.
	\item[] Rudik, I. 2018. \href{https://www.sciencedirect.com/science/article/pii/S0264999317315651}{Tradable Credit Markets for Intensity Standards}. \textbf{Economic Modelling} 72:202-215.
	\item[] Lemoine, D. and I. Rudik. 2017.  \href{http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2443594}{Steering the Climate System: Using Inertia to Lower the Cost of Policy}. \textbf{American Economic Review}  107(10):2947‐-57.
	\begin{itemize}
		\item[] Lemoine, D. and I. Rudik. 2020.  \href{http://papers.ssrn.com/sol3/papers.cfm?abstract_id=2443594}{Steering the Climate System: Reply}. \textbf{American Economic Review}  110(4):1238--41.
	\end{itemize}
	\item[] Lemoine, D. and I. Rudik. 2017. \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=2862211}{Managing Climate Change Under Uncertainty: Recursive Integrated Assessment at an Inflection Point}.  \textbf{Annual Review of Resource Economics}  9:117‐-142.
	\item[]  Burke, M., M. Craxton, C. D. Kolstad, C. Onda, H. Allcott, E. Baker, L. Barrage, R. Carson, K. Gillingham, J. Graff-Zivin, M. Greenstone, S. Hallegatte, W.M. Hanemann, G. Heal, S. Hsiang, B. Jones, D. L. Kelly, R. Kopp, M. Kotchen, R. Mendelsohn, K.Meng, G. Metcalf, J. Moreno-Cruz, R. Pindyck, S. Rose, I. Rudik, J. Stock, R. S. J. Tol. 2016. \href{http://science.sciencemag.org/content/352/6283/292.abstract}{Opportunities for Advances in Climate Change Economics}. \textbf{Science} 352(6283):292--93.
\end{itemize}
\vspace{-.2in}

\subsection{Working Papers}

\begin{itemize} % Reduce space between items
	\item[] \href{https://osf.io/preprints/socarxiv/usghb}{Heterogeneity and Market Adaptation to Climate Change in Dynamic Spatial Equilibrium} (with Gary Lyn, Weiliang Tan, Ariel Ortiz-Bobea)
	\item[] \href{https://www.nber.org/papers/w28250}{Lead Exposure Reduces Academic Performance: Intensity, Duration, and Nutrition Matter} (with Alex Hollingsworth, Mike Huang, and Nicholas Sanders)
\end{itemize}

\vspace{-.2in}

\subsection{Grants}
\begin{itemize}  \itemsep -1pt
	\item[] National Oceanic and Atmospheric Administration (\$400,000) \hfill Co-PI - 2020
	\item[] Cornell Atkinson Academic Venture Fund (\$175,000) \hfill PI - 2020
	\item[] Cornell NYC Visioning Grant (\$74,200) \hfill Co-PI - 2019
	\item[] NBER Economics of Energy Markets Grant (\$23,000) \hfill Co-PI - 2016
\end{itemize}

\vspace{-.2in}

\subsection{Seminars and Conferences (including scheduled)}\vspace{-.1in}
\paragraph{2021} University of Gothenburg, University of Massachusetts, Philadephia Federal Reserve, BIOECON, University of Arizona, Virtual Seminar on Climate Economics, Symposium on Natural Resource Governance for Young Scholars \vspace{-.2in}
\paragraph{2020} Penn State, Tennessee, WEAI Presidental Session (discussant), AERE, Global Open Seminar on Environmental Economics, NBER EEE Spring, Cornell Lab of Ornithology, ASSA (presenter, discussant) \vspace{-.2in}
\paragraph{2019} UC Davis, Carnegie Mellon University, UC San Diego, The Workshop in Environmental Economics and Data Science, University of Connecticut, ASSA (discussant) \vspace{-.2in}
\paragraph{2014--2018} Inter-American Development Bank, MIT CEEPR Fall Workshop, Heartland Environmental and Resource Economics Workshop, NBER EEE SI, Northeast Workshop on Energy Policy and Environmental Economics, Resources For the Future, Maryland AREC, ASSA, Minnesota APEC, East Carolina University, Cornell Dyson, EAERE, AERE, AAEA, Indiana University SPEA, Economics of Water and Energy Workshop (discussant), Colorado School of Mines, CU Environmental and Resource Economics Workshop, AERE, Fourth Annual Canadian Ph.D. and Early Career Workshop in Environmental Economics, NBER Economics of Energy Markets, UC Berkeley ARE, Stanford Research Frontiers in the Economics of Climate Change Workshop, The Occasional Workshop in Environmental and Resource Economics, NBER EEE SI, AERE, Iowa State University, University of Miami, Heartland Environmental and Resource Economics Workshop (poster), CU Environmental and Resource Economics Workshop, Western Economics Association Conference

\vspace{-.2in}

\subsection{Referee Service}\vspace{-.2in}
	Agricultural Economics,
	American Economic Journal: Economic Policy,
	American Economic Journal: Macroeconomics,
	American Economic Review,
	American Journal of Agricultural Economics,
	Climatic Change,
	Economics and Human Biology,
	Economic Journal,
	Energy Economics,
	Energy Journal,
	Environmental Research Letters,
	Environmental and Resource Economics,
	Journal of the Association of Environmental and Resource Economists,
	Journal of Economic Theory,
	Journal of Environmental Economics and Management,
	Journal of Health Economics,
	Journal of Policy Analysis and Management,
	Journal of Public Economics,
	National Science Foundation,
	Nature: Climate Change,
	Nature: Communications,
	Oxford Bulletin of Economics and Statistics,
	Proceedings of the National Academy of Sciences,
	Review of Economic Dynamics,
	Review of Environmental Economics and Policy,
	Science Advances,
	Society and Natural Resources

\vspace{-.2in}

\subsection{Professional Service}
\begin{itemize} \itemsep -1pt
	\item[] JAERE Editorial Council \hfill 2021--
	\item[] Computational Tools for Social Scientists Workshop \hfill 2020--
	\item[] AAEA Annual Meeting Reviewer \hfill 2017
\end{itemize}


\vspace{-.2in}

\subsection{University Service}
\begin{itemize} \itemsep -1pt
	\item[]	Graduate Studies Committee \hfill 2018--
\end{itemize}

\vspace{-.2in}

\subsection{Teaching}\vspace{-.2in}
\subsubsection{Cornell University}
\begin{itemize} \itemsep -1pt
	\item[] AEM 4510: Environmental Economics (undergraduate) \hfill 2021--
	\item[] AEM 4515: Business and Economics of Energy (undergraduate) \hfill 2018--2019
	\item[] AEM 6510: Environmental and Resource Economics (masters) \hfill 2018--
	\item[] AEM 7130: Dynamic Optimization (Ph.D.) \hfill 2019--
	\item[] AEM 7852: SEERE Seminar (workshop) \hfill 2018--
\end{itemize}\vspace{-.4in}
\subsubsection{Iowa State University}
\begin{itemize} \itemsep -1pt
	\item[] ECON 101: Principles of Microeconomics \hfill 2016--2017
	\item[] ECON 380: Environmental and Resource Economics \hfill 2017
	\item[] ECON 509: Applied Numerical Methods in Economics \hfill 2016--2017
\end{itemize}\vspace{-.4in}
\subsubsection{The University of Arizona}
\begin{itemize} \itemsep -1pt % Reduce space between items
	\item[] BNAD 301 Online: Global and Financial Economics and Strategies \hfill 2013, 2014
	\item[] ECON 323: The Economics of Sports \hfill 2013
	\item[] ECON 373: Environmental Economics \hfill 2012, 2014
\end{itemize}

\vspace{-.2in}

\subsection{Awards}
\begin{itemize}
	\item[] Cornell Dyson Outstanding Early Career Achievement Award \hfill 2021
\end{itemize}

\vspace{-.2in}

\subsection{Advising ($^*$ \textit{chair})  }
\vspace{-.2in}

\subsubsection{Ph.D.}\vspace{-.2in}
\paragraph{Current:} \textit{Luc Esprabens}$^*$; \textit{Mike Huang}$^*$; \textit{Weiliang Tan}$^*$; Marley Bonacquist-Currin; Muye Chen; Anjali Narang; Deyu Rao; Louis Sears; Hui Zhou
\vspace{-.4in}
\paragraph{2021:} \textit{Diego Cardoso$^*$ (Purdue Ag Econ AP)}; Yuanning Liang (Peking University AP); Lin Yang (HKUST AP)

\vspace{-.2in}

\subsubsection{Masters}\vspace{-.2in}
\paragraph{Current:} \textit{Henry Williams}$^*$, Byron Song, Delta Zhang, Terry Zhang
\vspace{-.4in}
\paragraph{2021:} \textit{Haotian Wu$^*$ (Ohio State AEDE Ph.D.)}; Visen Liu
\vspace{-.4in}
\paragraph{2020:} \textit{Jinge Li$^*$ (Yale Environment Ph.D.)}; Marley Bonacquist-Currin (Cornell DNRE Ph.D.); Yikuan Ji (Maryland AREC Ph.D.)
\vspace{-.4in}
\paragraph{2019:} Congyan Han (Wisconsin Urban Land Ph.D.)

\vspace{-.2in}

\subsubsection{Undergraduate}\vspace{-.2in}
\paragraph{2021:} \textit{Angela Zeng$^*$  (Duke Nicholas M.E.M.)}

\vspace{-.2in}

\subsection{Outreach}

\vspace{-.2in}

\subsubsection{Publications}
\begin{itemize} % Reduce space between items
	\item[] Keiser, D., G. Lade, and I. Rudik. \href{https://theconversation.com/ozone-pollution-in-us-national-parks-is-nearly-the-same-as-in-large-cities-100148}{Ozone Pollution in US National Parks is Nearly the Same as in Large Cities.} \textbf{The Conversation}.
	\item[] Lade, G. and I. Rudik. 2017. \href{https://www.card.iastate.edu/ag_policy_review/display.aspx?id=70}{Efficient Environmental Regulation in the Unconventional Oil Industry.} \textbf{Center for Agricultural and Rural Development Agricultural Policy Review}.
	\item[] Kling, C.L., R.W. Arritt, G. Calhoun, D.A. Keiser, J.M. Antle, J.G. Arnold, M. Carriquiry, I. Chaubey, P. Christensen, B. Ganapathysubramanian, P. Gassman, W. Gutowski, T.W. Hertel, G. Hoogenboom, E. Irwin, M. Khanna, P. Merel, D. Phaneuf, A. Plantinga, S. Polasky, P. Preckel,  S. Rabotyagov, I. Rudik, S. Secchi, A. Smith, A. Vanloocke, C. Wolter, W. Zhang, J.Zhao. 2016. \href{http://www.card.iastate.edu/products/publications/pdf/16wp563.pdf}{Research Needs and Challenges in the FEW System: Coupling Economic Models with Agronomic, Hydrologic, and Bioenergy models for Sustainabile Food, Energy, and Water Systems}. Center for Agricultural and Rural Development Working Paper 16-WP 563.
\end{itemize}

\vspace{-.2in}

\subsubsection{Media}
\begin{itemize} % Reduce space between items
	\item[] Hidden Curriculum Podcast \hfill 2021
	\item[] Science Sessions Podcast \hfill 2020
	\item[] Climate Reality Campus Corps Panel Speaker \hfill 2017
\end{itemize}
\subsection{Other}

\begin{itemize}
	\item[] \textbf{Professional Associations:} AEA, AERE
	\item[] \textbf{Training:} SCRiM Summer School for Sustainable Climate Risk Management, Fourth Annual Interdisciplinary School on Geoengineering
	\item[] \textbf{Citizenship:} U.S.
	\item[] \textbf{Languages:} English (native), American Sign Language (intermediate)
\end{itemize}
\hrule

\vspace{0.1in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	Last Updated On
%----------------------------------------------------------------------------------------


\centerline{\emph{Last Updated: \today}}
\pagebreak



\end{resume}



\end{document}
